---
title: "MiGEX report"
author: "MiGEX"
date: "2026-05-13"
output: pdf_document
params:
  pipeline_path: ""
  sample: ""
  fastp: ""
  amrfinder: ""
  bakta_gff: ""
  virulence: ""
  plasmids: ""
  mlst: ""
  mlst_log: ""
  mash: ""
  mash_details: ""
  quast: ""
  coverage: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r Packages loading, print=FALSE}
source(paste0(params$pipeline_path, "/scripts/plots_functions.R"))
library(ggplot2)
library(stringr)
library(ggpubr)
library(dplyr)
library(scales)
library(png)
library(grid)
library(cowplot)
library(jsonlite)
library(knitr)
```
Table with tools used in the pipeline and their version.  
Version of the pipeline.

\newpage

# Reads quality after filtering
Descriptive text to add and explain how data were obtained.

```{r Quality plots, fig.width=10,fig.height=5}
reads_quality_plot(params$fastp)
```

What does that mean ?  
filtered 
Q20, etc

# Assembly quality
Descriptive text to add and explain how data were obtained.

```{r Assembly Quality plots, fig.width=10,fig.height=5}
contigs_assembly_plot(params$quast, params$coverage, params$pipeline_path)
```

What does that mean ?

\newpage

# Organism identification
Descriptive text to add and explain how data were obtained.

```{r Table species identification}
identification_table <- identification_table(params$mash, params$mash_details)
kable(identification_table, align="c", digits = 5)
```

What does that mean ?  

# MLST analysis
```{r MLST data loading}
mlst_table <- mlst_table(params$mlst)
mlst_data <- mlst_table$data
```

The genome MLST is reported to be **`r mlst_data$ST`** with a score of 
**`r mlst_data$SCORE`% (`r mlst_data$STATUS`)** using the **`r mlst_data$SCHEME`**
scheme.

```{r MLST analysis table}
kable(mlst_table$table, align="c")
```

```{r MLST warning, results='asis'}
if (!is.na(mlst_log_warning(params$mlst_log))) {
  warning_msg <- mlst_log_warning(params$mlst_log)
  cat(paste("The following WARNING has been raised:", warning_msg))
}
```


*The scheme used might not be the one fitting the organism species. To force the 
MLST analysis to use the scheme of your choice, you can put the species code of 
your choice in the config file. Then delete the mlst folder and rerun the analysis.* 
