---
title: "MiGEX report"
author: "MiGEX"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme:
      version: 4
      bootswatch: flatly
    code_folding: hide
    self_contained: true
    css: css/style.css
params:
  pipeline_path: ""
  sample: ""
  fastp: ""
  amrfinder: ""
  virulence: ""
  plasmids: ""
  mlst: ""
  mlst_log: ""
  mash: ""
  mash_details: ""
  quast: ""
  coverage: ""
  reference_genome_id: ""
  reference_genome_length: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r Packages loading, print=FALSE}
source(paste0(params$pipeline_path, "/scripts/plots_functions.R"))
library(ggplot2)
library(stringr)
library(ggpubr)
library(dplyr)
library(scales)
library(png)
library(grid)
library(cowplot)
library(jsonlite)
library(knitr)
library(kableExtra)
```
Table with tools used in the pipeline and their version.  
Version of the pipeline.

\newpage

# Reads quality
Descriptive text to add and explain how data were obtained.

```{r Quality plots, fig.width=10,fig.height=5}
reads_quality_plot(params$fastp)
```

What does that mean ?  
filtered 
Q20, etc

# Assembly metrics
Descriptive text to add and explain how data were obtained.

```{r Assembly Quality plots, fig.width=10,fig.height=5}
contigs_assembly_plot(params$quast, params$coverage, params$pipeline_path)
```

```{r Comparison with reference, results='asis'}
message <- compare_to_reference(params$quast, params$reference_genome_id, params$reference_genome_length)
cat(message)
```

What does that mean ?

\newpage

# Identification
```{r Table species identification}
identification_table <- identification_table(params$mash, params$mash_details)
kable(identification_table, align="c", digits = 5, format = "html", 
      table.attr = "class='table table-striped table-hover'")
```

*This table presents the top matches between the query genome and the Mash 
pre-sketched RefSeq archive. Always review the analysis metrics before 
finalizing any identification.*

# MLST
```{r MLST data loading}
mlst_table <- mlst_table(params$mlst)
mlst_data <- mlst_table$data
```

The genome MLST is reported to be a **ST`r mlst_data$ST`** with a score of 
**`r mlst_data$SCORE`% (`r mlst_data$STATUS`)** using the **`r mlst_data$SCHEME`**
scheme.

```{r MLST analysis table}
kable(mlst_table$table, align="c", format = "html", 
      table.attr = "class='table table-striped table-hover'")
```

```{r MLST warning, results='asis'}
if (!is.na(mlst_log_warning(params$mlst_log))) {
  warning_msg <- mlst_log_warning(params$mlst_log)
  cat(paste("The following WARNING has been raised:", warning_msg))
}
```

*The scheme used might not be the one fitting the organism species. To force the 
MLST analysis to use the scheme of your choice, you can put the species code of 
your choice in the config file. Then delete the mlst folder and rerun the analysis 
(see documentation for more details).* 

# Antibiotic resistances
```{r AMR message, results='asis'}
amr_data <- amr_tables(params$amrfinder)

if (is.null(amr_data$resistances) || length(amr_data$resistances) == 0) {
  cat("No antibiotic resistances were detected.")
} else {
  cat("Resistances to the following antibiotics were found:\n\n")
  resistances <- as.character(unlist(amr_data$resistances))
  cat(paste0("- ", resistances, collapse = "\n"))
}
```

```{r AMR table}
if (!is.null(amr_data$amr_table)){
  amr_data$amr_table %>%
    kbl(caption = "AMR genes found",
        format = "html", 
        table.attr = "class='table table-striped table-hover'", 
        align="c") %>%
    kable_styling(font_size = 14,
                  bootstrap_options = c("striped", "hover"))
}
```

```{r Mutations table}
if (!is.null(amr_data$mutations_table)){
  amr_data$mutations_table %>%
    kbl(caption = "Relevant point mutations found",
        format = "html", 
        table.attr = "class='table table-striped table-hover'", 
        align="c") %>%
    kable_styling(font_size = 14,
                  bootstrap_options = c("striped", "hover"))
}
```

*Note that these are resistance predictions and may differ from the observed 
phenotype. Point mutations can only be analysed if the species is specified in 
the config file (see documentation for details). POINT_DISRUPT refers to point 
mutations that were not specifically curated but are likely to disrupt genes 
known to increase resistance when disrupted.*